External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

\begin{figure}\vspace{-0.1in}
\centering
\includegraphics[width=1\linewidth]{Flowchart.png}
\vspace{-0.25in}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-0.2in}
\label{fig2}
\end{figure}

@@

@@

The denoising of the given noisy image can be simultaneously done with the guided internal dictionary learning process. Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ8}) and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq. (\ref{equ9}), the latent clean patch of a noisy patch $\hat{\mathbf{y}}_{n,m}$ in PG $\mathbf{Y}_{n}$ is reconstructed as
\vspace{-2mm}
\begin{equation}\label{equ11}\vspace{-2mm}
\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
\end{equation}
where $\bm{\mu}_{n}$ is the group mean of Yn. The latent clean image is then reconstructed by aggregating all the reconstructed patches in all PGs. We perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.

We evaluate the performance of the proposed framework on denoising real noisy images. The denoising is simultaneously done with the guided internal dictionary learning process. We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity. In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction. Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq. for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ . Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by

where $n=1,...,N;m=1,...,M$.
\begin{table}\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Prior Guided Internal Prior Learning
\\
\quad \quad \quad for Real Noisy Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external PG prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $Ite = 1:IteNum$ \textbf{do}
\\
1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
\\
%\textbf{Guided Internal Subspace Selection:}
%\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
\\
\quad \ \ \ mean subtracted PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Subspace selection via Eq. (\ref{equ3});
\\
\quad\textbf{end for}
\\
%\textbf{Guided Internal Orthogonal Dictionary Learning:}
%\\
\quad\textbf{for} the PGs in each Subspace \textbf{do}
\\
4.\quad External PG prior Guided Internal Orthogonal
\\
\quad \ \ \ Dictionary Learning by solving (\ref{equ4});
\\
5.\quad Recover each patch in all PGs via Eq. (\ref{equ11});
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(Ite)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}
The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.

@@

In this section, we evaluate the performance of the proposed algorithm on real image denoising. To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior (Section 4.3). We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage} (Section 4.4).

@@

\subsection{Implementation Details}
Our proposed method contains two stages, the external prior learning stage and the external prior guided internal learning stage. In the first stage, we set $p = 6$ (so the patch size is $6\times 6 \times 3$), $M=10$ (the number of patches in a patch group (PG)), $W=31$ (so the window size for PG searching is $31\times31$, and $K=32$ (the number of Gaussians in Gaussian Mixture Model (GMM)). We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images. In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ4})), and $IteNum=4$ (the number of iterations for Alg. 1). All experiments are performed under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.

>>>>

@@

\begin{figure*}\vspace{-0.1in}
\centering
\includegraphics[width=0.8\linewidth]{Flowchart.png}
\vspace{-3mm}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-3mm}
\label{fig2}
\end{figure*}

@@

The denoising of the given noisy image can be simultaneously done with the guided internal dictionary learning process. Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ8}) and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq. (\ref{equ9}), the latent clean patch of a noisy patch $\hat{\mathbf{y}}_{n,m}$ in PG $\mathbf{Y}_{n}$ is reconstructed as
\vspace{-2mm}
\begin{equation}\label{equ11}\vspace{-2mm}
\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
\end{equation}
where $\bm{\mu}_{n}$ is the group mean of $\mathbf{Y}_{n}$. The latent clean image is then reconstructed by aggregating all the reconstructed patches in all PGs. We perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.
\begin{table}\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Prior Guided Internal Prior Learning
\\
\quad \quad \quad for Real Noisy Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external PG prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $Ite = 1:IteNum$ \textbf{do}
\\
1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
\\
%\textbf{Guided Internal Subspace Selection:}
%\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
\\
\quad \ \ \ mean subtracted PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Subspace selection via Eq. (\ref{equ3});
\\
\quad\textbf{end for}
\\
%\textbf{Guided Internal Orthogonal Dictionary Learning:}
%\\
\quad\textbf{for} the PGs in each Subspace \textbf{do}
\\
4.\quad External PG prior Guided Internal Orthogonal
\\
\quad \ \ \ Dictionary Learning by solving (\ref{equ4});
\\
5.\quad Recover each patch in all PGs via Eq. (\ref{equ11});
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(Ite)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}
The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.

@@

We evaluate the performance of the proposed algorithm on real-world noisy images \cite{crosschannel2016,ncwebsite}  in comparison with  state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage}.

\subsection{Implementation Details}

Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage. In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM. We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.

In the second stage, we set $r = 54$ (the number of atoms in the external sub-dictionaries); that is, we let the external sub-dictionary have the same number of atoms as the internal sub-dictionary to be learned. Our experiments show that setting $r$ between 27 and 81 will lead to very similar results. For other parameters, we set $\lambda=0.001$ (the sparse regularization parameter), $T = 2$ (the number of iterations for solving problem (\ref{equ4})), and $IteNum = 4$ (the number of iterations for Alg.1). All parameters of our method are fixed to all experiments, which are run under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.

@@
